Data preparation for team category analysis

### 2023-05-24 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Added section for routine teleworker and began section on team characteristics

1.  **All remote** - All team members are 100% remote
2.  **Routine teleworker** - All team members have
    `position_category_description`'s *Onsite Flexible* or *Offsite* and
    work at least two two days per pay period onsite.
3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
    defined by `position_category_description` in the roster data
4.  **Offsite** - All team members are *Offsite* as defined by team
    members `position_category_description` in the roster data
5.  **Onsite Required** - All team members are *Onsite Required* as
    defined by `position_category_description` in the roster data
6.  **Mixed position categories** - Team members are different position
    categories as as defined by `position_category_description` in the
    roster data
7.  **Primarily remote** - Teams that work remotely above the 95th
    percentile <!-- could be 75th -->
8.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
9.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
10. **Primarily onsite** - Teams that work remotely below the 5th
    percentile <!-- could be 75th -->

@@

```{r}
prep_h %>% 
  filter(rule_based_telework_onsite_minimum == 1) %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(rule_based_telework_onsite_minimum = n_distinct(person_id))
```

@@

```{r}
prep_xx <- cohort_first
```

>>>>

1.  **All remote** - All team members are 100% remote
2.  **Routine teleworker** - All team members who have
    `position_category_description`'s *Onsite Flexible* or *Offsite* and
    work at least two two days per pay period onsite.
3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
    defined by `position_category_description` in the roster data
4.  **Offsite** - All team members are *Offsite* as defined by team
    members `position_category_description` in the roster data
5.  **Onsite Required** - All team members are *Onsite Required* as
    defined by `position_category_description` in the roster data
6.  **Mixed position categories** - Team members are different position
    categories as as defined by `position_category_description` in the
    roster data
7.  **Primarily remote** - Teams that work remotely above the 95th
    percentile <!-- could be 75th -->
8.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
9.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
10. **Primarily onsite** - Teams that work remotely below the 5th
    percentile <!-- could be 75th -->

@@

Filter to team members who met the onsite minimum and count by `supervisor_e_mail_address`.

```{r}
prep_i <- 
  prep_h %>% 
  filter(rule_based_telework_onsite_minimum == 1) %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(rule_based_telework_onsite_minimum = n_distinct(person_id)) %>% 
  ungroup()
```

```{r}
prep_i %>% 
  skim()
```

From `cohort_panel` count number of team members with **Onsite flexible** or **Offsite** `position_category_description` by `supervisor_e_mail_address`.

```{r}
prep_j <- 
  cohort_panel %>% 
  filter(position_category_description == "Onsite Flexible" |
           position_category_description == "Offsite") %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(team_members_telework = n_distinct(person_id)) %>% 
  ungroup() 
```

```{r}
prep_j %>% 
  skim()
```

Full join and identify rows where all teleworking team members meet the minimum.

```{r}
prep_k <- 
  prep_i %>% 
  full_join(prep_j) %>% 
  mutate(
    rule_based_telework_onsite_minimum = case_when(rule_based_telework_onsite_minimum == team_members_telework ~ 1,
                    TRUE ~ 0)
  ) %>% 
  select(-team_members_telework)
```

```{r}
prep_k %>% 
  skim()
```

```{r}
prep_xx <-
  prep_building %>% 
  select(supervisor_e_mail_address) %>% 
  left_join(prep_k) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

### Mixed categories

From `cohort_panel` count team members by `position_category_description` and `supervisor_e_mail_address`, then filter to only `position_category_description`s that are **Onsite Flexible**, **Offsite**, or **Onsite Required**, then count `position_category_description` by `supervisor_e_mail_address`, then create `rule_based_mixed_position_category` identifying teams with more than one category, and last drop the temporary variable.

```{r}
prep_a <-
  cohort_panel %>% 
  group_by(supervisor_e_mail_address,position_category_description) %>% 
  summarise(team_members = n_distinct(person_id)) %>% 
  ungroup() %>% 
  filter(position_category_description == "Onsite Flexible" |
           position_category_description == "Offsite" |
           position_category_description == "Onsite Required") %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(temp_var = n_distinct(position_category_description)) %>% 
  ungroup() %>% 
   mutate(
     rule_based_mixed_position_category = case_when(temp_var > 1 ~ 1,
                                                    TRUE ~ 0)
     ) %>% 
  select(-temp_var)
```

Left join to `prep_building` selecting only `supervisor_e_mail_address`.

```{r}
prep_xx <-
  prep_building %>% 
  select(supervisor_e_mail_address) %>% 
  left_join(prep_a) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

```{r}
cohort_first %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(
    across(
      .cols = c(-where(is.Date),
                -employee_e_mail_address,
                -position_category_code,
                -employee_name,
                -supervisor_display_name,
                -date_day_of_week,
                -position_number,
                -business_line_2_letter_department_id),
      .fns = list(dist = n_distinct,mode = getmode),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
  select(-person_id_mode,
         -business_line_2_letter_department_id_dist) %>% 
  # skim()
  glimpse()
```

```{r}
cohort_first %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(
    across(
      .cols = c(grade),
      .fns = list(min = min, max = max),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
  # select(-person_id_mode,
  #        -business_line_2_letter_department_id_dist) %>% 
  # skim()
  glimpse()
```

```{r}
# prep_xx <- 
  cohort_ids %>% 
  select(supervisor_e_mail_address) %>% 
  distinct() %>% 
  inner_join(
    cohort_panel %>% 
      filter(date >= date_cohort_month_start & date <= date_cohort_month_end),
    by = c("supervisor_e_mail_address" = "employee_e_mail_address")
  ) %>% 
  skim()
```
